Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-03 doc/manuscript/manuscript.Rmd
add milgroom

@@

@@

# Supplementary Information {-}
\newpage

>>>>

We were unable to find evidence for sexual reproduction in any region. 
While the Australian population had a non-significant value of $\bar{r}_d$---which would suggest that we cannot reject the null hypothesis of random mating---the sample size was insufficient from which to draw conclusions [@agapow2001indices; @milgroom1996recombination].

@@

eh.

@@

# Supplementary Information {-}
